quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-09 paper-quollr.Rmd
Added main steps for hexbinning step wise

```{r, echo=TRUE}
calc_bins_y(
  nldr_obj = scurve_umap_obj, 
  bin1 = 15, 
  q = 0.1)
```

@@

@@

```{r, echo=TRUE}
df_bin_centroids <- extract_hexbin_centroids(
  centroids_data = hb_obj$centroids, 
  counts_data = hb_obj$std_cts
  )

>>>>

```{r, echo=TRUE}
bin_configs <- calc_bins_y(
  nldr_obj = scurve_umap_obj, 
  bin1 = 15, 
  q = 0.1)

bin_configs
```

@@

```{r, echo=TRUE}
all_centroids_df <- gen_centroids(
  nldr_obj = scurve_umap_obj, 
  bin1 = 15, 
  q = 0.1
  )

all_centroids_df
```

```{r, echo=TRUE}
all_hex_coord <- gen_hex_coord(
  centroids_data = all_centroids_df, 
  a1 = bin_configs$a1
  )

all_hex_coord
```

```{r, echo=TRUE}
umap_hex_id <- assign_data(
  nldr_obj = scurve_umap_obj, 
  centroids_data = all_centroids_df
  )

umap_hex_id
```

```{r, echo=TRUE}
std_df <- compute_std_counts(
  scaled_nldr_hexid = umap_hex_id
  )

std_df
```

```{r, echo=TRUE}
pts_df <- find_pts(
  scaled_nldr_hexid = umap_hex_id
  )

pts_df
```

@@

```{r, echo=TRUE}
df_bin_centroids <- extract_hexbin_centroids(
  centroids_data = all_centroids_df, 
  counts_data = hb_obj$std_cts
  )

### 2025-05-09 paper-quollr.tex
Added the error plot
Added main steps for hexbinning step wise

\begin{verbatim}
calc_bins_y(
  nldr_obj = scurve_umap_obj, 
  bin1 = 15, 
  q = 0.1)
\end{verbatim}

@@

@@

\begin{verbatim}
df_bin_centroids <- extract_hexbin_centroids(
  centroids_data = hb_obj$centroids, 
  counts_data = hb_obj$std_cts
  )

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-14-1}

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-15-1}

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-22-1}

>>>>

\begin{verbatim}
bin_configs <- calc_bins_y(
  nldr_obj = scurve_umap_obj, 
  bin1 = 15, 
  q = 0.1)

bin_configs
\end{verbatim}

@@

\begin{verbatim}
all_centroids_df <- gen_centroids(
  nldr_obj = scurve_umap_obj, 
  bin1 = 15, 
  q = 0.1
  )

all_centroids_df
\end{verbatim}

\begin{verbatim}
#> # A tibble: 240 x 3
#>    hexID     c_x     c_y
#>    <int>   <dbl>   <dbl>
#>  1     1 -0.1    -0.0892
#>  2     2 -0.0167 -0.0892
#>  3     3  0.0665 -0.0892
#>  4     4  0.150  -0.0892
#>  5     5  0.233  -0.0892
#>  6     6  0.316  -0.0892
#>  7     7  0.400  -0.0892
#>  8     8  0.483  -0.0892
#>  9     9  0.566  -0.0892
#> 10    10  0.649  -0.0892
#> # i 230 more rows
\end{verbatim}

\begin{verbatim}
all_hex_coord <- gen_hex_coord(
  centroids_data = all_centroids_df, 
  a1 = bin_configs$a1
  )

all_hex_coord
\end{verbatim}

\begin{verbatim}
#> # A tibble: 1,440 x 3
#>    hex_poly_id       x       y
#>          <int>   <dbl>   <dbl>
#>  1           1 -0.1    -0.0412
#>  2           1 -0.142  -0.0652
#>  3           1 -0.142  -0.113 
#>  4           1 -0.1    -0.137 
#>  5           1 -0.0584 -0.113 
#>  6           1 -0.0584 -0.0652
#>  7           2 -0.0167 -0.0412
#>  8           2 -0.0584 -0.0652
#>  9           2 -0.0584 -0.113 
#> 10           2 -0.0167 -0.137 
#> # i 1,430 more rows
\end{verbatim}

\begin{verbatim}
umap_hex_id <- assign_data(
  nldr_obj = scurve_umap_obj, 
  centroids_data = all_centroids_df
  )

umap_hex_id
\end{verbatim}

\begin{verbatim}
#> # A tibble: 5,000 x 4
#>     emb1  emb2    ID hexID
#>    <dbl> <dbl> <int> <int>
#>  1 0.707 0.839     1   205
#>  2 0.231 0.401     2   109
#>  3 0.232 0.215     3    65
#>  4 0.790 0.564     4   146
#>  5 0.761 0.551     5   146
#>  6 0.445 0.721     6   172
#>  7 0.900 0.137     7    58
#>  8 0.247 0.392     8   110
#>  9 0.325 0.542     9   141
#> 10 0.278 0.231    10    80
#> # i 4,990 more rows
\end{verbatim}

\begin{verbatim}
std_df <- compute_std_counts(
  scaled_nldr_hexid = umap_hex_id
  )

std_df
\end{verbatim}

\begin{verbatim}
#> # A tibble: 142 x 3
#>    hexID bin_counts std_counts
#>    <int>      <int>      <dbl>
#>  1    21         12     0.16  
#>  2    22         17     0.227 
#>  3    23         22     0.293 
#>  4    24         10     0.133 
#>  5    25          7     0.0933
#>  6    26         12     0.16  
#>  7    27          1     0.0133
#>  8    36         42     0.56  
#>  9    37         42     0.56  
#> 10    38         44     0.587 
#> # i 132 more rows
\end{verbatim}

\begin{verbatim}
pts_df <- find_pts(
  scaled_nldr_hexid = umap_hex_id
  )

pts_df
\end{verbatim}

\begin{verbatim}
#> # A tibble: 142 x 2
#>    hexID pts_list  
#>    <int> <list>    
#>  1    21 <int [12]>
#>  2    22 <int [17]>
#>  3    23 <int [22]>
#>  4    24 <int [10]>
#>  5    25 <int [7]> 
#>  6    26 <int [12]>
#>  7    27 <int [1]> 
#>  8    36 <int [42]>
#>  9    37 <int [42]>
#> 10    38 <int [44]>
#> # i 132 more rows
\end{verbatim}

@@

\begin{verbatim}
df_bin_centroids <- extract_hexbin_centroids(
  centroids_data = all_centroids_df, 
  counts_data = hb_obj$std_cts
  )

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-19-1}

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-20-1}

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-28-1}
